Tables

### 2018-03-29 code/tables.rmd
Complete heterogeneity table
Including effect sizes and standardized/unstandardized

summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
  kable_styling() %>% 
  footnote(threeparttable = TRUE,
           general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).")

@@

    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2],      r_ci.ub = I2_2[3]))

@@

  data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]) #output is for smd, r, and 1 raw difference
}

#Apply function to data
res <- dat %>% 
  filter(!rs == "RRR5") %>% #Remove RRR5 for now because have not been able to extract sufficient data for it
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
  mutate(dif = s_I2 - r_I2) #Gives us the difference between the two

@@

#Add rs to the data-frame
het <- dat %>% 
  select(rs, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Mean diff.",
                              r = "Correlation",
                              'Raw mean difference' = "Mean diff.",
                              'Risk difference' = "OR / RD"),
         effect_type = ifelse(effect %in% clarify, "OR / RD", effect_type)) %>% 
  arrange(desc(s_I2)) #sort by rs and I2 for standardized effect

@@

##Heterogeneity in preregistered multi-lab psychology studies
```{r heterogeneity-table}
library(kableExtra)
het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "Effect type", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 3, "Standardized" = 3, "Unstandardized" = 3, " " = 1)) #%>% 
  # footnote(threeparttable = TRUE,
           # general = "'OR / RD' indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns. Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios. For correlations the standardized version correspond to Fisher's r-to-z transformed correlation and unstandardized to raw correlations. All original authors used raw correlations in their meta-analyzes. For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences. Original authors used different approaches for mean differences. RRR5 I have not yet been able to extract a measure of variance for, hence the NAs. Effects were estimated in metafor using REML with the 'knha' correction.")

```
**Note**: "OR / RD" indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns. Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios. For correlations the standardized version correspond to Fisher's r-to-z transformed correlation and unstandardized to raw correlations. All original authors used raw correlations in their meta-analyzes. For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences. Original authors used different approaches for mean differences. RRR5 I have not yet been able to extract a measure of variance for, hence the NAs. Effects were estimated in metafor using REML with the "knha" correction.

>>>>

summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
  kable_styling(position = "left") %>% 
  footnote(threeparttable = TRUE,
           general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).")
```

@@

    return(data.frame(eff_size = fit$b[[1]],
                      s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], 
                      r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]))

@@

  data.frame(eff_size = fit$b[[1]], #standardized effect (point estimate)
             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], #standardized I2 + CI
             r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]) #unstandardized I2 + CI
}

#Apply function to data
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
  mutate(dif = s_I2 - r_I2) #Gives us the difference between the two

@@

#Add rs to the data-frame
het <- dat %>% 
  select(rs, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Mean diff.",
                              r = "Correlation",
                              'Raw mean difference' = "Mean diff.",
                              'Risk difference' = "OR / RD"),
         effect_type = ifelse(effect %in% clarify, "OR / RD", effect_type)) %>% 
  arrange(desc(s_I2)) #sort by I2 for standardized effect
```

##Heterogeneity in preregistered multi-lab psychology studies
```{r heterogeneity-table}
library(kableExtra)
het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  add_header_above(c(" " = 4, "Standardized" = 3, "Unstandardized" = 3, " " = 1)) %>%
  footnote(threeparttable = TRUE,
           general = "'OR / RD' indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns. Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios. For correlations the standardized version correspond to raw correlations.  For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences. Original authors used different approaches for mean differences. RRR5 I have not yet been able to extract a measure of variance for, hence the NAs. Effects were estimated in metafor using REML with the 'knha' correction. Estimate column are point estimates of standardized effect sizes.")

@@
